
---
title: "Exploratory Anaylsis Report"

date: "11/13/2020"

output: html_document
---



**Main field/domain:** How different age groups use social media.

**Why are you interested in this field/domain:** It is personal to us, it is how we communicate to people consistently. Social media is something that us as a society uses everyday, regardless of their age. We are intrigued by the differences in how people use social media depending on their age because we know first hand experience the differences in the way we use social media compared to our parents.





[View Dataset](https://raw.githubusercontent.com/info201b-au20/info201-final-group-project/gh-pages/Effects%20of%20Social%20Media%20(Responses).csv)







**Summary paragraph:**




**Chart 1:**

source("scripts/First Chart.R")

**Chart 2:**

source("scripts/Second Chart.R")

**Chart 3:**


**Effects of Social Media Table data:**

```{r echo=FALSE,message=FALSE}
source("scripts/Table of Summary Information.R")
```

The table below shows the changes we made to the original dataset and we decided to keep the columns:

* *Age:* The age of each survey participant

* *Social_media_accounts:* Social media accounts of each participant

* *Hours_spent_on_social_media_in_a_day:* The amount of hours spent on social media in a day

* *Preferred_type_of_communication:* How they wish to communicate with others

```{r echo=FALSE, message=FALSE}
library(knitr)
kable(newDF)
```







