
---
title: "Exploratory Anaylsis Report"

date: "11/13/2020"

output: html_document
---
```{r echo=FALSE,message=FALSE}
source("scripts/Third Chart.R")
```


**Main field/domain:** How different age groups use social media.

**Why are you interested in this field/domain:** It is personal to us, it is how we communicate to people consistently. Social media is something that us as a society uses everyday, regardless of their age. We are intrigued by the differences in how people use social media depending on their age because we know first hand experience the differences in the way we use social media compared to our parents.





[View Dataset](https://raw.githubusercontent.com/info201b-au20/info201-final-group-project/gh-pages/Effects%20of%20Social%20Media%20(Responses).csv)







**Summary paragraph:**




**Chart 1:**
```{r echo=FALSE, message=FALSE}
source("scripts/First Chart.R")
```
**Chart 2:**






This simple scatter plot gives a precise visual about how different age groups
ranging from 14-23 use social media to communicate. This chart was used to show
the preferred methods of communication because it shows more than one way an
an age group preferred to communicate. This makes it easier to see the trend of
communication between different age groups. The trend of this chart shows that
people between the ages of 18 - 19 prefer all the types of communication methods
while age groups between 14- 16, and 21-3 tend to prefer half or less than half
to communicate. The different preferred types of communication types go up
with age then slowly go back down after the age of 20.

```{r pref_type, echo=FALSE}
plot(pref_type)
```

**Effects of Social Media Table data:**

```{r echo=FALSE, message=FALSE}
source("scripts/Table of Summary Information.R")
```

The table below shows the changes we made to the original dataset and we decided to keep the columns:

* *Age:* The age of each survey participant

* *Social_media_accounts:* Social media accounts of each participant

* *Hours_spent_on_social_media_in_a_day:* The amount of hours spent on social media in a day

* *Preferred_type_of_communication:* How they wish to communicate with others

```{r echo=FALSE, message=FALSE}
library(knitr)
kable(newDF)
```
